---
title: "CO2 Emission Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: 
      version: 4
      bootswatch: cerulean
vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(ggplot2)
library(miniUI)
library(DT)
countries_by_fuel = read.csv("E:\\DV Project\\data\\co2-emissions-by-fuel-line.csv", header=TRUE)
countries_annual_co2_emission = read.csv("E:\\DV Project\\data\\annual-co2-emissions-per-country.csv", header=TRUE)
countries_year_wise_co2_change = read.csv("E:\\DV Project\\data\\absolute-change-co2.csv", header=TRUE)
total_ghg_emissions = read.csv("E:\\DV Project\\data\\total-ghg-emissions.csv", header=TRUE)
percapita_ghg_emissions = read.csv("E:\\DV Project\\data\\per-capita-ghg-emissions.csv", header=TRUE)
methane_emissions = read.csv("E:\\DV Project\\data\\methane-emissions.csv", header=TRUE)
nitrous_oxide_emissions = read.csv("E:\\DV Project\\data\\nitrous-oxide-emissions.csv", header=TRUE)
global_co2_concentration = read.csv("E:\\DV Project\\data\\global-co-concentration-ppm.csv", header=TRUE)
global_methane_concentration = read.csv("E:\\DV Project\\data\\ch4-concentration.csv", header=TRUE)
global_nitrous_oxide_concentration = read.csv("E:\\DV Project\\data\\n2o-concentration.csv", header=TRUE)
```

CO2 Emission By Fossil Fuels{data-orientation=columns}
===================================

Column{.sidebar data-width=200}
-----------------------------------

<br>
<strong>This graph shows the amount of CO2 generated by different types of fossil fuels in the selected country.</strong>
<br>

```{r}
distinct_coutries_fuel = countries_by_fuel %>% distinct(Entity) %>% pull()
selectInput("country_choice", label = h5("Select Country"),
            choices = distinct_coutries_fuel, selected = "Afghanistan")
```

row {data-width=350}
---------------------------------
### <strong>Fossil Fuel CO2 Emissions</strong>{data-height=600}   

```{r, echo=FALSE}

miniContentPanel(
  renderPlot({
    input_df = countries_by_fuel %>% filter(Entity == input$country_choice)
    inputCountry <- paste(input$country_choice)
    ggplot(input_df, aes(x=Year))+
      geom_line(aes(y = CO2.emissions.from.oil, color="Oil"), size=1.5)+
      geom_line(aes(y = CO2.emissions.from.flaring, color="Flaring"), size=1.5)+
      geom_line(aes(y = CO2.emissions.from.cement, color="Cement"), size=1.5)+
      geom_line(aes(y = CO2.emissions.from.coal, color="Coal"), size=1.5)+
      geom_line(aes(y = CO2.emissions.from.gas, color="Gas"), size=1.5)+
      geom_line(aes(y = CO2.emissions.from.other.industry, color="Other Industry"), size=1.5)+
      scale_color_manual(values = c("darkred", "steelblue", "green", "darkorange", "#0036CC", "yellow"))+                          ggtitle(paste(inputCountry), "CO2 Emissions By fossil Fuels, Yearly") +
      labs(x="Year", y="CO2 Emissions from Fossil Fuels\n(metric tonnes per year)")+ 
      theme(axis.title.y = element_text(size=14, family="Trebuchet MS", color="#666666")) +
      theme(plot.title = element_text(size=26, family="Trebuchet MS", face="bold", hjust=0, color="#666666")) +
      theme(axis.text = element_text(size=16, family="Trebuchet MS"))
  }),
  

renderDT({
      input_df = countries_by_fuel %>% filter(Entity == input$country_choice)
      datatable(input_df, extensions = c('Responsive'), 
            options = list(responsive = TRUE))
}),scrollable = TRUE)

```

Global CO2 Emissions
====================================


Column{.sidebar data-width=200}
-----------------------------------

<br>
<strong>This graph shows the amount of CO2 generated by different countries annually, with absolute CO2 emission growth.</strong>
<br>

```{r}
distinct_coutries_annual_co2 = countries_annual_co2_emission %>% distinct(Entity) %>% pull()
selectInput("annual_country_choice", label = h5("Select Country"),
            choices = distinct_coutries_annual_co2, selected = "Afghanistan")
  
renderUI ({ 
  annual_input_df = countries_annual_co2_emission %>% filter(Entity == input$annual_country_choice)
    sliderValue = as.vector(annual_input_df$Year)
            sliderInput("yearrange", label = h5("Year"), 
            min = min(as.numeric(annual_input_df$Year)), 
            max = max(as.numeric(annual_input_df$Year)), 
            value = 100,
            animate = TRUE
            )})
```

Column{data-width=400}
-----------------------------------
### <strong>Annual CO2 Emissions</strong>

```{r}
miniContentPanel(
  
  renderPlot({
      annual_input_df = countries_annual_co2_emission %>% filter(Entity == input$annual_country_choice)
      annual_input_df = annual_input_df %>% filter(Year <= input$yearrange)
      ggplot(data = annual_input_df, aes(x = Year, y = Annual.CO2.emissions))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
  }),
  renderDT({
      annual_input_df = countries_annual_co2_emission %>% filter(Entity == input$annual_country_choice)
      annual_input_df = annual_input_df %>% filter(Year <= input$yearrange)
      datatable(annual_input_df, extensions = c('Responsive'), 
            options = list(responsive = TRUE))
}),scrollable = TRUE)

```

Column{data-width=400}
-----------------------------------
### <strong>Bar Plot of Annual CO2 Emissions</strong>

```{r}
renderPlot({
      annual_input_df = countries_annual_co2_emission %>% filter(Entity == input$annual_country_choice)
      annual_input_df = annual_input_df %>% filter(Year <= input$yearrange)
      ggplot(data = annual_input_df, aes(x = Year, y = Annual.CO2.emissions))+
          geom_bar(stat="identity", fill="white", color="blue")+
          theme_minimal()
})
```

### <strong>Annual Absolute CO2 Emission Growth </strong>

```{r}
renderPlot({
      country_annual_change_year_wise = countries_year_wise_co2_change %>% filter(Entity == input$annual_country_choice)
      country_annual_change_year_wise = country_annual_change_year_wise = country_annual_change_year_wise %>% filter(Year <= input$yearrange)
      ggplot(data = country_annual_change_year_wise, aes(x = Year, y = Annual.co2.growth.absolute))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})

```


GHG Emission
===================================

Column{.sidebar data-width=200}
-----------------------------------

<br>
<strong>This page consists different graphs showing Country Wise GHG emission, Per Capital GHG Emission,
Annual Methane Emission and Annual Nitrous Oxide Emissions.</strong>
<br>


```{r}
distincy_countries_total_ghg_emissions = total_ghg_emissions %>% distinct(Entity) %>% pull()
selectInput("total_gfg_country_choice", label = h5("Select Country"),
            choices = distincy_countries_total_ghg_emissions, selected = "Afghanistan")
  
renderUI ({ 
  total_ghg_input_df = total_ghg_emissions %>% filter(Entity == input$total_gfg_country_choice)
    sliderValue = as.vector(total_ghg_input_df$Year)
            sliderInput("ghgyearrange", label = h5("Year"), 
            min = min(as.numeric(total_ghg_input_df$Year)), 
            max = max(as.numeric(total_ghg_input_df$Year)), 
            value = 100,
            animate = TRUE
            )})
```


Column{data-width=500}
-----------------------------------

### <strong>Country Wise GHG Emission</strong>

```{r}
renderPlot({
      country_ghg_change_year_wise = total_ghg_emissions %>% filter(Entity == input$total_gfg_country_choice)
      country_ghg_change_year_wise = country_ghg_change_year_wise = country_ghg_change_year_wise %>% filter(Year <= input$ghgyearrange)
      ggplot(data = country_ghg_change_year_wise, aes(x = Year, y = Total.GHG.emissions.including.LUCF))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})
```

Column{data-width=300}
-----------------------------------

### <strong>Per Capita GHG Emission</strong>
```{r}
renderPlot({
      country_percapita_ghg_change_year_wise = percapita_ghg_emissions %>% filter(Entity == input$total_gfg_country_choice)
      country_percapita_ghg_change_year_wise = country_percapita_ghg_change_year_wise = country_percapita_ghg_change_year_wise %>% filter(Year <= input$ghgyearrange)
      ggplot(data = country_percapita_ghg_change_year_wise, aes(x = Year, y = Total.including.LUCF.percapita))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})
```

### <strong>Methane Emission</strong>
```{r}
renderPlot({
      methane_change_year_wise = methane_emissions %>% filter(Entity == input$total_gfg_country_choice)
      methane_change_year_wise = methane_change_year_wise = methane_change_year_wise %>% filter(Year <= input$ghgyearrange)
      ggplot(data = methane_change_year_wise, aes(x = Year, y = Total.including.LUCF.CH4.emissions))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})
```

### <strong>Nitrous Oxide Emission</strong>

```{r}
renderPlot({
      nitrous_oxide_change_year_wise = nitrous_oxide_emissions %>% filter(Entity == input$total_gfg_country_choice)
      nitrous_oxide_change_year_wise = nitrous_oxide_change_year_wise = nitrous_oxide_change_year_wise %>% filter(Year <= input$ghgyearrange)
      ggplot(data = nitrous_oxide_change_year_wise, aes(x = Year, y =Total.including.LUCF.N2O.emissions))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})
```

Atmospheric Concentration
===================================

Column{.sidebar data-width=200}
-----------------------------------

<br>
<strong>This page shows the global CO2 concentration and Global Concentration of other GFGs. i.e. Methane and Nitrous Oxide.</strong>
<br>

```{r}
renderUI ({ 
    sliderValue = as.vector(global_co2_concentration$Year)
            sliderInput("concentrationyearrange", label = h5("Global CO2 Year Input"), 
            min = min(as.numeric(global_co2_concentration$Year)), 
            max = max(as.numeric(global_co2_concentration$Year)), 
            value = 1,
            animate = TRUE
            )
})

renderUI({
      sliderValue = as.vector(global_methane_concentration$Year)
            sliderInput("othergasesyearrange", label = h5("Global Methane/Nitrous Oxide Year Input"), 
            min = min(as.numeric(global_methane_concentration$Year)), 
            max = max(as.numeric(global_methane_concentration$Year)), 
            value = 1750,
            animate = TRUE
            )
})
```


Column{data-width=500}
-----------------------------------

### <strong>Global CO2 Concentration</strong>

```{r}
renderPlot({
      global_co2_concentration = global_co2_concentration %>% filter(Year <= input$concentrationyearrange)
      ggplot(data = global_co2_concentration, aes(x = Year, y =CO2.concentrations.world))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})
```

Column{data-width=300}
-----------------------------------

### <strong>Methane Concentration</strong>
```{r}
renderPlot({
      global_methane_concentration = global_methane_concentration %>% filter(Year <= input$othergasesyearrange)
      ggplot(data = global_methane_concentration, aes(x = Year, y =CH4.concentration.world))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})
```

### <strong>Nitrous Oxide Concentration</strong>
```{r}
renderPlot({
      global_nitrous_oxide_concentration = global_nitrous_oxide_concentration %>% filter(Year <= input$othergasesyearrange)
      ggplot(data = global_nitrous_oxide_concentration, aes(x = Year, y =N2O.concentrations.world))+
      geom_line(color = "#0099f9", size = 1) + geom_point(color = "#0099f9", size = 3)
})
```




About Us{data-orientation=rows}
====================================

### <strong>About Us</strong> {data-height=300}
<div style="width:80%;margin:auto;">
<h3 style="text-align: center;">CO2 Emission Dashboard</h3>
#### About Project
Across this project we have used different visualization methods to create a dashboard, which can help people visualise the increasing trend of CO2 and other greenhouse gases around the world.
This project also focuses on helping people visualise the trend across specific countries. 
The dataset used in this project is extremely detailed and contains a lot of information which has been edited and sorted to make this entire visualization project possible. The aforementioned dataset contains over 20,000 rows and 50+ columns. It has detailed information of all the countries of the world with a wide range of information regarding CO2 and Greenhouse gases emissions(such as growth rate, countries’ GDP, per capita emissions, etc.).

#### About Data: 
  > CO2 Emission Data from Kaggle. 
  
  In this project we are using  CO2 and Greenhouse Emission data, which is downloaded from kaggle and ourworldindata.org.
  This dataset contains 55 columns and 20,000+ rows.
  This dataset contains year wise data of all the countries of the world. This dataset         includes wide range of information regarding CO2 emission (i.e. Growth rate, countries GDP,    CO2 emission per capita, etc.)

#### Team:
* Abhinav Tripathi 19BCE0548
* Aditya Pagaria 19BCE0348


</div>

```{r}
```

